First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-28 eg6-letters/coherent/dvcs_he4_prl_liuti.tex
Comments from S. Liuti

\RequirePackage{lineno}
%\documentclass[preprint,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
\documentclass[twocolumn,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%
\def\Dirac#1{#1\hskip-5pt/}
%
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
\expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
\expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
\renewenvironment{#1}%
{\linenomath\csname old#1\endcsname}%
{\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
\patchAmsMathEnvironmentForLineno{#1}%
\patchAmsMathEnvironmentForLineno{#1*}}%
\AtBeginDocument{%
\patchBothAmsMathEnvironmentsForLineno{equation}%
\patchBothAmsMathEnvironmentsForLineno{align}%
\patchBothAmsMathEnvironmentsForLineno{flalign}%
\patchBothAmsMathEnvironmentsForLineno{alignat}%
\patchBothAmsMathEnvironmentsForLineno{gather}%
\patchBothAmsMathEnvironmentsForLineno{multline}%
}

@@

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of coherent deeply virtual 
Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from the CEBAF machine at Jefferson Lab incident on a $^4$He gas 
target in the center of the CEBAF large acceptance spectrometer. A new radial 
time projection chamber (RTPC) was used to detect the recoiling $^4$He
nuclei and ensure the exclusivity of the process. The measured beam spin 
asymmetries are larger than that observed on the proton in the same kinematic 
domain. Since $^4$He is a spin zero target, we were able to extract, in a 
completely model independent way, the real and imaginary parts of the $^4$He 
Compton form factors, $\cal H_A$, which are functions of the generalized parton 
distribution $H_A$. This pioneering measurement of coherent deeply virtual 
Compton scattering on the $^4$He nucleus, with a fully exclusive final state 
via nuclear recoil tagging, leads the way toward 3D imaging of the partonic 
structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

Rich information on quantum chromodynamics (QCD) can be extracted from the 
internal structure of hadrons. In the recent past, development of the 
generalized parton distribution (GPD) framework has offered a possibility to 
obtain new information about the momentum and spatial degrees of freedom of the 
quarks and gluons inside hadrons 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
In impact parameter space the GPDs are indeed interpreted as a tomography of 
the transverse plane for partons carrying a certain longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.

The most promising way to access GPDs experimentally is through the measurement 
of deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
electroproduction of a real photon.  While other processes are known to be 
sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
has been the focus of worldwide efforts 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
involving several accelerator facilities such as Jefferson Lab, HERA and  CERN.  
The vast majority of these measurements focused on the study of proton 
structure and allowed for extraction of the three-dimensional picture of the 
nucleon (for details on the formalism, see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
This framework is also applicable to nuclei, giving access to completely new 
information about nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
Study of the 3D structure of nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\caption{Representation of the leading order hand-bag diagram of the DVCS 
process off $^4$He.}
\label{fig:diags}
\end{figure}

One must overcome two major experimental challenges in measuring coherent 
nuclear DVCS, $eA\rightarrow^\prime A^\prime\gamma$. First, the cross section 
of coherent scattering is suppressed due to the nuclear form factor, and 
second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
FIG.~\ref{fig:diags} illustrates the hand-bag diagram for coherent DVCS on 
$^4$He. Similar to the proton case, at large virtual photon's 4-momentum square 
$Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$ (in terms 
of the electron, $k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag 
diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
hard part includes the photon-quark interaction and is calculable in 
perturbative QCD. The non-perturbative part is parametrized in terms of GPDs, 
which embed the partonic structure of the hadron. The GPDs depend on the three 
variables $x$, $\xi$, and $t$ as introduced in FIG.~\ref{fig:diags}. The 
parameter $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$, $\nu=k^0-k^{0\prime}$, and 
$M$ is the proton mass. The parameter $x$ is the quark's internal loop momentum 
fraction and cannot be accessed experimentally. In the experiment we measure 
Compton form factors (CFF) \cite{Guidal:2013rya}, for which their real and 
complex amplitudes are defined at leading order as

@@

Until now, the only available data on nuclear DVCS was from the HERMES 
experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based 
only on kinematic cuts on the measured scattered electron and real photon. That 
measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
but the mixing of the coherent and incoherent processes could affect the
measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
of the low-energy recoil nucleus is the best way to guarantee that the nucleus 
remains intact. The CEBAF large acceptance spectrometer (CLAS) in Hall-B at 
Jefferson Lab has been previously used for DVCS measurements on nucleon
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.

@@

The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
polarization) at an energy of 6.064 GeV. The data were collected over 40 days 
using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center 
of CLAS. For DVCS experiments, the CLAS baseline design \cite{Mecking:2003zu} 
is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC 
extends the photon detection acceptance of CLAS to polar angles as low as 
4$^{\circ}$. The low-energy M\o{}ller electrons produced in the target form a 
very high rate background that is suppressed by a 5 Tesla solenoid magnet 
placed around the target.

In our kinematics, the recoil $^4$He nuclei produced in DVCS have a low average 
momentum around 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light RTPC to complement CLAS. Presented in FIG.~\ref{fig:RTPC} are a 
picture of RTPC installed in the experimental hall and a diagram showing the 
basic detection technique. The $^4$He gaseous target, a $25$ cm long Kapton 
straw with $27~\mu$m thick wall, was part of the RTPC assembly and installed on 
the axis of the detector. The RTPC was calibrated specifically for the 
detection of $^4$He nuclei using elastic scattering with a 1.2~GeV electron 
beam.

@@

To ensure the interaction occurs at the partonic level and the DVCS handbag 
diagram is dominant, we select events with $Q^{2}$ greater than 1 
$GeV^{2}/c^{2}$. Exclusivity of the coherent DVCS reaction is optimized by 
applying a set of cuts on the following kinematic variables: the co-planarity 
angle ($\Delta \phi$), \textit{i.e.}, the angle between the ($\gamma,\gamma^*$) 
and ($\gamma^*$,$^4$He$'$) planes, the missing energy, the missing mass 
squared, the missing transverse momentum of the $e'^4$He$'\gamma$ system, the 
missing mass squared of the $e'^4$He$'$ system, and the angle ($\theta$) 
between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
The most relevant of these cuts are presented in FIG.~\ref{fig:kin-cuts}, which 
shows 3$\sigma$ cuts except for the missing energy (which appears to be too 
large and for which we reduced the cut window to [-0.45,0.5] GeV).  We also 
reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
two photons. About 3200 events pass these requirements. Their kinematic 
distributions are shown in FIG.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the coherent DVCS events candidate. The shaded 
distributions represent the events which passed all the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied exclusivity 
cuts. The distributions from left to right and from top to bottom are: $\Delta 
\phi$, missing energy, missing mass squared and the cone angle ($\theta$) 
between the measured and the calculated photons.}
\label{fig:kin-cuts}
\end{figure}

@@

The DVCS and well-known Bethe-Heitler (BH) processes, where the real 
photon is emitted by the incoming or the outgoing lepton, have the same final 
state and are indistinguishable. The amplitude of real photon 
electroproduction is a sum of the amplitudes of these two processes. The BH 
amplitude is defined by the target form factors, while the DVCS amplitude is 
a combination of the form factors and GPDs. At our kinematics, the cross 
section of real photon electroproduction is dominated by the BH 
contribution, while the DVCS contribution is very small. Its effect is however
enhanced in the observables sensitive to the interference term, {\it e.g.} 
beam spin asymmetry. The three terms entering the cross section calculation,
the BH and DVCS amplitudes squared and their interference term, 
can be decomposed into a finite sum of Fourier harmonics in the azimuthal angle
$\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes, as
shown for the nucleon in \cite{Belitsky:2001ns} and for the spin-zero targets
in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the beam-spin 
asymmetry of a spin-zero hadron can be expressed as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ and depend on the GPD $H_A$.  
The kinematic factors $\alpha_i$ depend on azimuthal angle $\phi$, the nuclear 
form factor $F_A(t)$, $Q^2$ and $x_B$. These factors are written as
\begin{align}
   \alpha_0 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi), \\
   \alpha_1 (\phi) & = c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi), \\ 
   \alpha_2 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
      C_{++}(0) +  C_{++}(1) cos(\phi) \right), \\
   \alpha_3 (\phi) &= \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
      {\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
      \epsilon^2},
\end{align}
where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) the $^4$He 
(nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, and $\mathcal{P}_1(\phi)$ and $\mathcal 
{P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
$c_0^{DVCS}$, $c_{0,1}^{INT}$ and $s_1^{INT}$ are the Fourier coefficients of 
the BH, and $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics 
in the leptonic tensor.  The explicit expressions of these terms can be found 
in \cite{Belitsky:2008bz} and show that, by using the $\sin(\phi)$ and 
$\cos(\phi)$ contributions, it is possible to extract $\Im m(\mathcal{H}_{A})$ 
and $\Re e(\mathcal{H}_{A})$ from the beam spin
asymmetry.

@@

Due to limited statistics, dependence on the kinematical variables $Q^2$, 
$x_B$, and $t$ has been studied separately. In FIG.~\ref{fig:alu}, $A_{LU}$ for 
the three sets of binning is presented. The curves on the plots are fits with 
the function presented in Eq.~\ref{eq:A_LU-coh}, where the real and imaginary 
parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit.  In 
FIG.~\ref{fig:alu90} the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
are compared to theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. The model relies on the impulse approximation and uses 
advanced spectral functions of nuclei. The calculations are at slightly 
different kinematics than our data but still provide some guidance. The 
experimental results appear to have larger asymmetries than the calculations.  
These differences may arise from nuclear effects, such as long-rage 
interactions, which are not taken into account in the model.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and $t$ 
   bins (bottom panel).  The error bars represent the statistical 
   uncertainties. The gray bands represent the systematic uncertainties, 
   including the normalisation uncertainties. The red curves are the results of 
our fits with the form of equation \ref{eq:A_LU-coh}.}
\label{fig:alu}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU_90.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
   the $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
   \cite{Airapetian}, the colored curves represent theoretical calculations 
   %\cite{HERMES_BSA}, the colored curves represent theoretical calculations 
   from \cite{simonetta_2}.}
\label{fig:alu90}
\end{figure}

@@

>>>>

\RequirePackage{lineno}
%\documentclass[preprint,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
\documentclass[twocolumn,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
\usepackage{color,graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%
\def\Dirac#1{#1\hskip-5pt/}
%
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
\expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
\expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
\renewenvironment{#1}%
{\linenomath\csname old#1\endcsname}%
{\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
\patchAmsMathEnvironmentForLineno{#1}%
\patchAmsMathEnvironmentForLineno{#1*}}%
\AtBeginDocument{%
\patchBothAmsMathEnvironmentsForLineno{equation}%
\patchBothAmsMathEnvironmentsForLineno{align}%
\patchBothAmsMathEnvironmentsForLineno{flalign}%
\patchBothAmsMathEnvironmentsForLineno{alignat}%
\patchBothAmsMathEnvironmentsForLineno{gather}%
\patchBothAmsMathEnvironmentsForLineno{multline}%
}

@@

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of coherent Deeply Virtual Compton 
Scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from the CEBAF machine at Jefferson Lab incident on a $^4$He gas 
target in the center of the CEBAF Large Acceptance Spectrometer. A new 
Radial Time Projection Chamber was used to detect the recoiling $^4$He
nuclei and ensure the exclusivity of the process. The measured Beam Spin 
Asymmetries are larger than that observed on the proton in 
the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
extract, in a completely model independent way, the real and imaginary parts of the $^4$He Compton Form Factors, $\cal H_A$, which are functions of the Generalized Parton Distribution $H_A$. 
This pioneering measurement of coherent Deeply Virtual Compton Scattering on the $^4$He nucleus, with a fully exclusive final state via nuclear recoil tagging, leads the way toward 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

Rich information on Quantum Chromodynamics (QCD) can be extracted from the internal structure 
of hadrons. In the recent past, development of the Generalized Parton 
Distributions (GPDs) framework has offered a possibility to obtain new 
information about the momentum and spatial degrees of freedom of the quarks and 
gluons inside hadrons 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
transverse plane for partons carrying a 
%certain 
\textcolor{magenta}{given fraction of the proton}
longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.

The most promising way to access GPDs experimentally is through the measurement 
of Deep Virtual Compton Scattering (DVCS), i.e.  the hard exclusive 
electroproduction of a real photon.  While other processes are known to be 
sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
has been the focus of worldwide efforts 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN.  The vast majority of these measurements focused on the study of proton 
structure and allowed \textcolor{magenta}{for an} extraction of the tomography of the nucleon (for details 
on the formalism, see 
\textcolor{magenta}{\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya,Kumericki:2016ehc}}).
This framework is also applicable to nuclei, giving access to completely new 
information about nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
\textcolor{magenta}{A} study of the 3D structure of nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\caption{Representation of the leading order handbag diagram of the 
DVCS process off $^4$He.}
\label{fig:diags}
\end{figure}

One must overcome two major experimental challenges in measuring coherent 
nuclear DVCS, $eA\rightarrow^\prime A^\prime\gamma$. First, the cross section 
of coherent scattering is suppressed due to the nuclear form factor, and 
second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence. 
Figure \ref{fig:diags} 
illustrates the hand bag diagram for coherent DVCS on $^4$He.  Similarly to the 
proton case, at large virtual photon's 4-momentum square $Q^2=-(k-k')^{2}$ and 
small squared momentum transfer $t=(p-p')^{2}$ (in terms of the electron, 
$k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag diagram can be 
factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The hard part 
includes the photon-quark interaction and is calculable in perturbative QCD.  
The non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron. The GPDs depend on the three variables $x$, 
$\xi$ and $t$ as introduced in Figure \ref{fig:diags}. The parameter $\xi$
relates to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and  
$\nu=k^0-k^{0\prime}$, the $t$ is squared momentum transfer to the target. The 
parameter $x$ is the quark's internal loop momentum fraction and cannot be 
accessed experimentally. In the experiment we measure the Compton Form
Factors (CFF) \cite{Guidal:2013rya} \textcolor{magenta}{which are} complex amplitudes defined as:

@@

Until now, the only available data on nuclear DVCS was from the 
HERMES experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based only on 
kinematic cuts on the measured scattered electron and real photon. That 
measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
but the mixing of the coherent and incoherent processes could affect the
measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
of the low-energy recoil nucleus is the best way to guarantee the nucleus 
remains intact and that the reaction did not occur on a bound nucleon. The 
CEBAF Large Acceptance Spectrometer (CLAS) in Hall-B at JLab is already 
optimized for DVCS measurements 
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.

@@

The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
polarization) at energy of 6.064 GeV. The data were collected over 40 days 
using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center of CLAS. For DVCS 
experiments, the CLAS baseline design \cite{Mecking:2003zu} is supplemented 
with an inner calorimeter (IC) and a solenoid. The IC extends the photon 
detection acceptance of CLAS to polar angles as low as 4$^{\circ}$. The 
low-energy M\o{}ller electrons produced in the target form a very high rate 
background that is suppressed by a 5 Tesla solenoid placed around the target.

In our kinematics, the recoil $^4$He nuclei produced in DVCS have a low average 
momentum around 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light RTPC to complement CLAS. In Figure~\ref{fig:RTPC} a picture of 
RTPC installed in the experimental hall, and the rendering showing detector 
components and the $^4$He detection concept are presented. The $^4$He gaseous 
target, a $25$ cm long Kapton straw with $27~\mu$m thick wall, was part of the RTPC
assembly and installed on the axis of the detector. The RTPC was calibrated specifically for the detection 
of $^4$He nuclei using elastic scattering with a 1.2~GeV electron beam.

@@

To ensure the interaction occurs at the partonic level and the DVCS handbag 
diagram is dominant, we select events with $Q^{2}>1~[GeV^{2}/c^{2}]$.  
Exclusivity of the coherent DVCS reaction is optimized by applying a set of 
cuts on the following kinematic variables: the co-planarity angle ($\Delta 
\phi$), \textit{i.e.}, the angle between the ($\gamma,\gamma^*$) and 
($\gamma^*,^4He'$) planes, the missing energy, the missing mass squared, the 
missing transverse momentum of the $e'^4He'\gamma$ system, the missing mass 
squared of the $e'^4He'$ system, and the angle ($\theta$) between the measured 
photon and the missing momentum of the $e'^4He'$ system. The most relevant of 
these cuts are presented in Figure~\ref{fig:kin-cuts}, which shows 3$\sigma$ 
cuts except for the missing energy (which appears to be too large and for which 
we reduced the cut window to [-0.45,0.5] GeV).  We also reject events where a 
$\pi^0$ is identified by invariant mass reconstruction of two photons.  After 
these requirements, we have about 3200 DVCS events left, and Figure 
\ref{fig:kin-coverage} presents their kinematic distributions in 
($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the coherent DVCS events candidate. The shaded 
distributions represent the events which passed all the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied exclusivity 
cuts. The distributions from left to right and from top to bottoms are: $\Delta 
\phi$, missing energy, missing mass squared and the cone angle ($\theta$) 
between the measured and the calculated photons.}
\label{fig:kin-cuts}
\end{figure}

@@

The DVCS and %well-known 
Bethe-Heitler (BH) processes, where the real 
photon is emitted by the incoming or the outgoing lepton, have the same final 
state and are indistinguishable. The amplitude of real photon 
electroproduction is a sum of the amplitudes of these two processes. The BH 
amplitude is defined by the target form factors, while the DVCS amplitude is 
a combination of the form factors and GPDs. At our kinematics, the cross 
section of real photon electroproduction is dominated by the BH 
contribution, while the DVCS contribution is very small. Its effect is however
enhanced in the observables sensitive to the interference term, {\it e.g.} 
beam spin asymmetry. The three terms entering the cross section calculation,
the BH and DVCS amplitudes squared and their interference term, 
%can be decomposed into a finite sum of Fourier harmonics is written in terms of 
\textcolor{magenta}{depend on} the azimuthal angle
$\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes, as
shown for the nucleon in \cite{Belitsky:2001ns} and for the spin-zero targets
in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the beam-spin 
asymmetry ($A_{LU}$) of a spin-zero hadron can be expressed as:
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ that depends on the GPD 
$H_A$. In Eq.~\ref{eq:A_LU-coh}, $\phi$ is the azimuthal angle between the 
($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The kinematic factors $\alpha_i$
%depend 
\textcolor{magenta}{were written in Ref.\cite{Belitsky:2008bz})} as a function of  
Fourier harmonics in the azimuthal angle $\phi$, the nuclear form factor 
$F_A(t)$, and \textcolor{magenta}{the kinematic invariants}, $Q^2$, $x_B$, \textcolor{magenta}{$x_{A} = \displaystyle\frac{x_{B}M_{N}}{M_{A}}$, 
$y=\displaystyle\frac{Q^2}{2x_{A} M_A E_{beam}}$,
and $\epsilon = \displaystyle\frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$, where $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass.} 
%These factors are written as:
%\begin{align}
%   \alpha_0 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi), \\
 %  \alpha_1 (\phi) & = c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi), \\ 
%   \alpha_2 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
%      C_{++}(0) +  C_{++}(1) cos(\phi) \right), \\
%   \alpha_3 (\phi) &= \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
%      {\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
%      \epsilon^2},
%\end{align}
%where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) is the $^4$He 
%(nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
%$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, $\mathcal{P}_1(\phi)$ and $\mathcal 
%{P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
%$c_0^{DVCS}$, $c_{0,1}^{INT}$ and $s_1^{INT}$ are the Fourier coefficients of 
%the BH, and $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics 
%in the leptonic tensor.  
The explicit expressions of these terms can be found 
in \cite{Belitsky:2008bz} and show that, by using the $\sin(\phi)$ and 
$\cos(\phi)$ contributions, it is possible to extract $\Im m(\mathcal{H}_{A})$ 
and $\Re e(\mathcal{H}_{A})$ from the beam spin
asymmetry.

@@

Due to limited statistics, dependence on the kinematical variables $Q^2$, 
$x_B$, and $t$ has been studied separately. In Figure \ref{fig:alu}, $A_{LU}$ 
for the three sets of binning is presented. The curves on the plots are fits 
with the function presented in Eq.~\ref{eq:A_LU-coh}, where the real and 
imaginary parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit. 
In Figure \ref{fig:alu90} the $Q^2$, $x_{B}$, and $-t$-dependencies of the 
fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and 
$-t$-dependencies are compared to theoretical calculations performed by 
S.~Liuti and K.~Taneja \cite{simonetta_2}. 
%The model relies on the impulse 
%approximation and uses advanced spectral functions of nuclei. 
\textcolor{magenta}{The model takes into account 
the effect on the quark distribution of the high virtuality/off-shellness of the nucleon with 
four-momentum squared not equal to the square of their mass.}
The calculations 
are at slightly different kinematics than our data but still provide some 
guidance. The experimental results appear to have \textcolor{magenta}{a larger asymmetry  than the 
calculation in the $x_B=0.307$ bin.  This difference arises from the theoretical 
uncertainty in the determination of the crossing
point between the antishadowing region, where the parton nuclear distribution is larger than the nucleon one, and 
the EMC effect region, where the nuclear effect reverses its sign.}
%These differences may arise from nuclear effects, such as 
%long-rage interactions, which are not taken into account in the model.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and 
   $-t$ bins (bottom panel).  
   The error bars represent the statistical uncertainties. The gray 
   bands represent the systematic uncertainties, including the normalisation 
   uncertainties. The red curves are the results of our fits with the form of 
   equation \ref{eq:A_LU-coh}.}
\label{fig:alu}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU_90.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $-t$-dependencies (right) of
   the $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
   \cite{Airapetian}, the colored curves represent theoretical calculations 
   %\cite{HERMES_BSA}, the colored curves represent theoretical calculations 
   from \cite{simonetta_2}.}
\label{fig:alu90}
\end{figure}

@@

\bibitem{Kumericki:2016ehc} 
  K.~Kumericki, S.~Liuti and H.~Moutarde,
  %``GPD phenomenology and DVCS fitting : Entering the high-precision era,''
  Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 157 (2016)
